---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# creditriskau - Australian credit risk capital tools

You will be able to calculated credit risk capital related quantities using this package. These reflect the standards outlined in [APRA's credit risk prudential standards](http://www.apra.gov.au/adi/PrudentialFramework/Pages/prudential-standards-and-guidance-notes-for-adis.aspx), and consequently reflects the Australian implementation of the [Basel III capital standards](http://www.bis.org/bcbs/basel3.htm). 

## Retail exposures

The following illustrates the capital ratios associated with retail exposures with different credit risk characteristics.

```{r retail_example}
library(tidyverse)
library(creditriskau)
x <- seq(0.01, 0.99, by = 0.03)
pd <- rep(x, 3)
lgd <- 0.20
sub_class <- rep(c("mortgage", "qrr", "other"), each = length(x))
k <- retail_capital(pd, lgd, sub_class)
df <- tibble(pd, lgd, sub_class, k)
ggplot(df, aes(x = pd, y = k, colour = sub_class)) + 
  geom_point() +
  theme_minimal() +
  labs(x = "PD", y = "Capital ratio", colour = "Sub-asset class")
```

## Non-retail exposures

The following illustrates the capital ratios associated with non-retail exposures with different credit risk characteristics.

```{r non_retail_example}
size <- rep(c(1, 10, 100), each = length(x))
k <- non_retail_capital(pd, lgd, size, 1, FALSE)
df <- tibble(pd, lgd, size, k)
ggplot(df, aes(x = pd, y = k, colour = as.character(size))) + 
  geom_point() +
  theme_minimal() +
  labs(x = "PD", y = "Capital ratio", colour = "Size (A$m)")
```

Capital ratios for specialised lending facilities subject to slotting can be accessed using the `slotting_capital()` function.

## Counterparty credit risk exposures

To be completed.
